---
title: "Data Dictionary - Airline Baggage Complaints Dataset"
author: "Muskan Gupta"
date: "`r Sys.Date()`"
output: html_document
---

# Data Dictionary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(readr)
library(ggplot2)

# Install and load kableExtra if not installed
if (!requireNamespace("kableExtra", quietly = TRUE)) {
  install.packages("kableExtra")
}
library(kableExtra)

# Load the dataset
baggage_complaints <- read_csv("/Users/muskangupta/Downloads/baggagecomplaints.csv")

data_dict <- data.frame(
  Variable_Name = c("Airline", "Date", "Month", "Year", "Baggage", "Scheduled", "Cancelled", "Enplaned"),
  Readable_Variable_Name = c("Airline Name", "Date of Record", "Month of Observation", "Year of Record", "Number of Baggage Complaints", "Flights Scheduled", "Flights Cancelled", "Passengers Enplaned"),
  Measurement_Units = c("Categorical", "mm/yyyy", "Numeric", "Numeric", "Numeric", "Numeric", "Numeric", "Numeric"),
  Allowed_Values = c("Various airline names", "01/2004 - latest", "1-12", "2004 - latest year available", "0 - any positive integer", "0 - any positive integer", "0 - any positive integer", "0 - any positive integer"),
  Definition = c(
    "Name of the airline company reporting baggage complaints.",
    "The month and year when the data was recorded.",
    "The numerical representation of the month (January = 1, February = 2, etc.).",
    "The year corresponding to the complaint records.",
    "Number of baggage complaints recorded for the airline in that month.",
    "Number of flights scheduled for that airline in the given month.",
    "Number of flights that were canceled in that month.",
    "Total number of passengers who boarded flights for the airline in that month."
  ),
  Description = c(
    "This variable contains the names of airline companies that reported baggage complaints.",
    "This variable represents the month and year when the data was collected.",
    "A numeric value representing the month of the year.",
    "A numeric value representing the year the record belongs to.",
    "Represents the number of baggage-related complaints recorded for the airline.",
    "Shows how many flights were scheduled in that month.",
    "Indicates how many flights were canceled during that month.",
    "Denotes the total number of passengers who boarded flights for that airline during the month."
  )
)

kable(data_dict, format = "html") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))
```

# Data Collection Methodology
This data is sourced from airlines and aviation authorities which monitor complaints related to baggage. These are consolidated every month and prepared for reporting. The dataset captures complaints records from all airlines so that the entire spectrum of airline services performance with regard to baggage disposition is captured.


# Why does this data set intrigue you?
This dataset is intriguing because it reveals some level of airline service quality and customer satisfaction. Monitoring of baggage complaints can help detect trends, seasonality, and potential problems in airline operations. It can also help improve passenger experience by identifying and solving most dissatisfied issues.

# Data Visualization

```{r, echo=TRUE}
# Plot baggage complaints over time
ggplot(baggage_complaints, aes(x = Date, y = Baggage)) +
  geom_line(color = "blue") +
  labs(title = "Baggage Complaints Over Time", x = "Date", y = "Number of Complaints") +
  theme_minimal()
```

# References
- [Kaggle - Airline Baggage Complaints Time Series Dataset](https://www.kaggle.com/datasets/gabrielsantello/airline-baggage-complaints-time-series-dataset)
- [USGS Example Data Dictionaries](https://www.usgs.gov/products/data-and-tools/data-management/data-dictionaries)
